SNEQ_Lynott_example

### 2017-10-19 NSEQ_Lynott_example.Rmd
Lynott example - Finished draft, including adding the data file, a description file, and a jamovi file. Current example replicates Lynott SPSS .sav+.sps but not values in paper. Notification letter to the authors has been composed.

In order to distinguish between these two hypotheses, we calculate the TOST. We first need to define our SESOI (and thus, our bounds). In this case, it is not really clear what an objective cirterion for the smallest effect size of interest could be. However, we could decide that we do not care about an effect if the difference is smaller than the smallest effect we could potentially detect with the current sample. This essentially means that we use the critical z value (~1.96 in a two-tailed test with an alpha of 0.05) as our bounds. To convert the critical z value to the critical difference in proportions for this study, we multiply critical z with the standard error:

```{r}
se     <- sqrt((0.512 * (1 - 0.512)) / 427 + (0.579 * (1 - 0.579)) / 434)  # Calculate the (unpooled) standard error
crit.z <- qnorm(1 - (0.05 / 2))  # Determine the critical z for a two-tailed test with alpha = 0.05

@@

Using the TOSTtwo.prop function in the TOSTER package in R, we can then calculate the TOST by insterting the summary statistics from Lynott et al. (2014), assuming an aplha of 0.05, and using +/- the value of `crit.diff` (`r crit.diff`) as our equivalence bounds. We find that the TOST is non-significant, t(96.62) = 0.72, p = 0.24. Thus, in addition to begin statistically different from zero, we cannot reject the possibility that the true difference really is larger than our SESOI.

@@

TOSTtwo.prop(prop1 = 0.512, 
             prop2 = 0.579, 
             n1    = 427, 
             n2    = 434, 
             low_eqbound  = -crit.diff, 
             high_eqbound = crit.diff, 
             alpha = 0.05)

@@

>>>>

In order to distinguish between these two hypotheses, we calculate the TOST. We first need to define our SESOI (and thus, our bounds). In this case, it is not really clear what an objective cirterion for the smallest effect size of interest could be. However, since this is a replication, we could decide that we do not care about an effect if the difference is smaller than the smallest effect that the original study could detect. This essentially means that we use the critical z value (~1.96 in a two-tailed test with an alpha of 0.05) as our bounds. To figure out what difference corresponds to a critical z in the original study, we multiply critical z with the standard error:

```{r}
se     <- sqrt((0.75 * (1 - 0.75)) / 26 + (0.46 * (1 - 0.46)) / 27)  # Calculate the (unpooled) standard error
crit.z <- qnorm(1 - (0.05 / 2))  # Determine the critical z for a two-tailed test with alpha = 0.05

@@

Using the TOSTtwo.prop function in the TOSTER package in R, we can then calculate the TOST by insterting the summary statistics from Lynott et al. (2014), assuming an aplha of 0.05, and using +/- the value of `crit.diff` (`r crit.diff`) as our equivalence bounds.

@@

#  We first load the data and exclude cases to only include cases that did not meet the authors' exclusion criteria. 
lynott.data <- read.csv("SNEQ_Lynott_example_data.csv")
lynott.data <- lynott.data[lynott.data$include1 == 1,]

#  We then calculate the summary statistics from the data that we need in the TOST calculation below
n.hot        <- sum(lynott.data$packtype == 1)
n.cold       <- sum(lynott.data$packtype == 0)
selfish.hot  <- sum(lynott.data$selfish[lynott.data$packtype == 1] == 1, na.rm = TRUE) / n.hot
selfish.cold <- sum(lynott.data$selfish[lynott.data$packtype == 0] == 1, na.rm = TRUE) / n.cold

#  We can now run the TOST!
tost <- TOSTtwo.prop(prop1 = selfish.hot, 
                     prop2 = selfish.cold, 
                     n1    = n.hot, 
                     n2    = n.cold, 
                     low_eqbound  = -crit.diff, 
                     high_eqbound = crit.diff, 
                     alpha = 0.05)

@@

We find that the TOST is `r tost$TOST_outcome`, z = `r round(min(abs(c(tost$TOST_z1, tost$TOST_z2))), 2)`, p `r ifelse(round(max(abs(c(tost$TOST_p1, tost$TOST_p2))), 2) >= 0.01, paste("=", round(max(abs(c(tost$TOST_p1), tost$TOST_p2))), 2), "< 0.01")`. Thus, in addition to beinn statistically different from zero, we cannot reject the possibility that the true difference really is larger than our SESOI.
